Title

### 2020-12-06 documents/DraftReport.Rmd
Edited introduction

Understanding the processes that control population dynamics in wild populations is a critical component of conservation but is frequently constrained by missing demographic information, uncertainty in data, and temporally or spatially misaligned datasets (citation). Integrated population models (IPMs) are an increasingly popular tool in ecology that offer release from these limitations by providing a framework to combine disparate datasets in a single, unified analysis (Schaub & Abadi 2011). This approach can provide several advantages like estimation of otherwise non-identifiable parameters, improved precision in parameter estimation, and [spatio-temporal inference] (citation). These advances have practical benefits for resource managers that must make decisions based on limited available information. As IPMs become more widely used, however, it is critical that they are robustly evaluated.

@@

We aim to improve our understanding of this important statistical approach, particularly for passerine bird life history. In this study, we simulate data to examine IPM performance across a range of scenarios where data informing key demographic parameters are sparse or missing. We simulate three datasets for a for a theoretical passerine: 1) census counts, 2) reproductive output, and 3) mark-recapture (MR) of banded individuals. We then systematically vary the uncertainty in our abundance and MR data and run the integrated models under scenarios where demographic parameters like survival and fecundity are high or low. By identifying scenarios where IPMs do not lead to improved precision or cannot estimate unidentifiable parameters, we refine our understanding of the mechanisms underlying IPMs and can better identify when they may serve as a useful tool.

>>>>

Understanding the processes that control population dynamics in wild populations is a critical component of conservation but is frequently constrained by missing demographic information, uncertainty in data, and temporally or spatially misaligned datasets (Schaub & Abadi 2011, Zipkin & Saunders 2017). Integrated population models (IPMs) are an increasingly popular tool in ecology that offer release from these limitations by providing a framework to combine disparate datasets in a single, unified analysis (Schaub & Abadi 2011). This approach can provide several advantages like estimation of otherwise non-identifiable parameters, improved precision in parameter estimation, and [spatio-temporal inference] (citation). These advances have practical benefits for resource managers that must make decisions based on limited available information. As IPMs become more widely used, however, it is critical that they are robustly evaluated.

@@

We aim to improve our understanding of this important statistical approach, particularly for passerine bird life history. In this study, we simulate data to examine IPM performance across a range of scenarios where data informing key demographic parameters are sparse or missing. We simulate three datasets for a for a theoretical passerine: 1) count surveys, 2) reproductive output, and 3) mark-recapture (MR) of banded individuals. We then run integrated models systematically 1) omitting nest or MR data, 2) varying the detection probabilities of the abundance and MR datasets, and 3) creating scenarios where demographic parameters like survival and fecundity are high or low. By examining model performance, we aim to identify scenarios where IPMs do not lead to improved precision or cannot estimate unidentifiable parameters. In doing so, we refine our understanding of the mechanisms underlying IPMs and can better identify when they may serve as a useful tool.
